% !TeX program = lualatex
\documentclass[12pt, a4paper]{article}

% ==========================================
% 字体与排版设置 (完全遵循 Handbook 要求)
% ==========================================
\usepackage{fontspec}
% Handbook §9.2 允许 "Calibri 12 or a close equivalent"。
% Linux 下使用 Google 开源的 Carlito —— 专为与 Calibri metric-compatible 设计，官方认可的等效字体。
% 已通过 apt 包 fonts-crosextra-carlito 系统安装，fontspec 自动通过 fontconfig 查找。
% 如在 Windows/macOS 最终出稿，可改为 \setmainfont{Calibri}。
\setmainfont{Carlito}

% 页边距设置：四周均至少 2cm
\usepackage[left=2.5cm, right=2.5cm, top=2.5cm, bottom=2.5cm]{geometry}

% 1.5 倍行距
\usepackage{setspace}
\onehalfspacing

% 左对齐 (不两端对齐 / Not fully justified)
\raggedright
\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}

% ==========================================
% 常用宏包
% ==========================================
\usepackage{graphicx}                                          % 插入图片
\graphicspath{{figures/}{figures/provisional/}}                % 图片搜索路径
\usepackage{float}                                             % 图/表 [H] 强制定位
\usepackage{placeins}                                          % \FloatBarrier 卡住图不跨章
\usepackage[font=small,labelfont=bf,labelsep=period]{caption}  % 图题：粗 "Fig. 4.1."  + 小号描述
\usepackage{subcaption}                                        % 多子图 (a)(b)(c)
\usepackage{booktabs}                                          % 三线表 \toprule \midrule \bottomrule
\usepackage{siunitx}                                           % \SI{15000}{\hertz} 等 SI 单位
\usepackage{titlesec}                                          % 调整标题样式

% 参考文献设置 (要求使用 biber 和 IEEE 格式)
\usepackage[backend=biber, style=ieee]{biblatex}
\addbibresource{references.bib}

\usepackage{hyperref}                                          % 超链接 (放在最后)

% ==========================================
% 文档正文开始
% ==========================================
\begin{document}

% ------------------------------------------
% Title Page (根据 Report Template)
% ------------------------------------------
\begin{titlepage}
    \centering
    \vspace*{2cm}
    
    {\fontsize{24pt}{28pt}\selectfont \textbf{B-BOT: A WiFi-Enabled Self-Balancing Wheel-Legged Robot with ROS 2 Vision Teleoperation}\par}
    
    \vspace{2cm}
    {\Large \textbf{Third Year Individual Project – Final Report}\par}
    
    \vspace{1cm}
    {\large May 2026\par}
    
    \vspace{3cm}
    % TODO: 把 XXXXXXX 替换为学号的前 7 位（不含第 8 位）
    {\large Your Identification Number: \textbf{XXXXXXX}\par}

    \vspace{3cm}
    {\large Supervisor: \textbf{Dr Liam Marsh}\par}
    
    \vfill
\end{titlepage}

% ------------------------------------------
% 前置部分 (不计入 35 页)
% ------------------------------------------
\newpage
\section*{Abstract}
This is the abstract. Max 1 page.

\newpage
\section*{Declaration of Originality}
I hereby confirm that this dissertation is my own original work unless referenced clearly to the contrary...

\newpage
\section*{Intellectual Property Statement}
The author of this thesis owns certain copyright or related rights in it...

\newpage
\tableofcontents

\newpage
\listoffigures
\listoftables

\newpage
% ==========================================
% 正文部分 (上限 35 页)
% ==========================================
\section{Introduction}
\subsection{Background and motivation}
Write your background here.

\subsection{Aims and objectives}
Write your objectives here.

\subsection{Report structure}
Write report structure here.

\subsection{Project Management}
Discuss how you planned and managed the project using Gantt charts, CPD, etc.

\section{Literature review}
Compare LQR, PID, VMC and embedded ROS architectures~\cite{grasser2002joe,chan2013review,klemm2019ascento,han2009adrc,pratt2001vmc,madgwick2011imu,mahony2008complementary,macenski2022ros2}.

\section{Methods}
Discuss the system architecture, hardware, and algorithms.

\section{Results and discussion}
Show the performance of your wheel-legged robot.

\section{Conclusions and future work}
\subsection{Conclusions}
\subsection{Future work}

% ==========================================
% 参考文献
% ==========================================
\newpage
\printbibliography

% ==========================================
% 附录 (不计入 35 页)
% ==========================================
\newpage
\appendix
\section{Preliminary Project Proposal}
Your project outline here.

\section{Project Plan and Gantt Chart}
Include Gantt chart image here.

\section{Risk Register}
Include HSE risk register here.

\section{Continuing Professional Development (CPD) Log}
Include your CPD log here.

\section{Health \& Safety Risk Assessment}
Include safety risk assessment here.

\section{Software Repository Link \& README}
\textbf{Repository Link:} \url{https://github.com/your-username/b-bot} \\
Include the README content here.

\end{document}
